---
title: "data analysis"
author: "Siyu Wang"
date: "12/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(broom)
install.packages("lsr")
library(lsr)
library(car)
```

Data analysis for VR+PC
```{r}
data<-read.csv("PC_VR.csv") %>% select(-char)
```

```{r}
data_long<-gather(data,measure,score,word:word_weighted)
```

```{r}
summary<-data_long %>% group_by(condition,measure) %>% summarise(mean=mean(score),sd=sd(score),se=sd/sqrt(n()), upper=mean+se*1.96, lower=mean-se*1.96)
```

```{r}
group_means <- data_long %>%
  group_by(condition, measure) %>%
  summarise(score = mean(score))

ggplot(data_long, aes(condition, score, color = condition)) +
  geom_jitter(alpha = .2) +
  geom_violin(aes(fill = condition), alpha = .2) +
  facet_wrap(~measure) +
  geom_point(data = group_means, size = 2) +
  labs(x = "measure", y = "score") +
  theme_bw()
```

t-test for word (in task):
```{r}
result_word <- t.test(data %>% filter(condition == "VR") %>% pull(word),
                      data %>% filter(condition == "PC") %>% pull(word), paired = TRUE) %>%
  tidy()
```

effect size for word:
```{r}
cohensD(data %>% filter(condition == "VR") %>% pull(word),
                      data %>% filter(condition == "PC") %>% pull(word),method="paired")
```

t-test for weighted word (in-task):
```{r}
result_word_weighted <- t.test(data %>% filter(condition == "VR") %>% pull(word_weighted),
                      data %>% filter(condition == "PC") %>% pull(word_weighted), paired = TRUE) %>%
  tidy()
```

effect size for weighted word:
```{r}
cohensD(data %>% filter(condition == "VR") %>% pull(word_weighted),
                      data %>% filter(condition == "PC") %>% pull(word_weighted),method="paired")
```

t-test for speed (pre-task):
```{r}
result_prespeed <- t.test(data %>% filter(condition == "VR") %>% pull(speed_pre),
                      data %>% filter(condition == "PC") %>% pull(speed_pre), paired = TRUE) %>%
  tidy()
```

effect size for speed (pre-task):
```{r}
cohensD(data %>% filter(condition == "VR") %>% pull(speed_pre),
                      data %>% filter(condition == "PC") %>% pull(speed_pre),method="paired")
```

Data analysis for PC+Mask:
```{r}
data2<-read.csv("PC_MASK.csv") %>% select(-char)
```

Data analysis for VR+PC
```{r}
data_long2<-gather(data2,measure,score,PreSpeedbb:word_weighted)
```

```{r}
summary2<-data_long2 %>% group_by(condition,measure) %>% summarise(mean=mean(score),sd=sd(score),se=sd/sqrt(n()), upper=mean+se*1.96, lower=mean-se*1.96)
```

```{r}
group_means <- data_long2 %>%
  group_by(condition, measure) %>%
  summarise(score = mean(score))

ggplot(data_long2, aes(condition, score, color = condition)) +
  geom_jitter(alpha = .2) +
  geom_violin(aes(fill = condition), alpha = .2) +
  facet_wrap(~measure) +
  geom_point(data = group_means, size = 2) +
  labs(x = "measure", y = "score") +
  theme_bw()
```
t-test for word (in task):
```{r}
result_word2 <- t.test(data2 %>% filter(condition == "PC") %>% pull(word),
                      data2 %>% filter(condition == "Mask") %>% pull(word), paired = TRUE) %>%
  tidy()
```

effect size for word:
```{r}
cohensD(data2 %>% filter(condition == "PC") %>% pull(word),
                      data2 %>% filter(condition == "Mask") %>% pull(word),method="paired")
```

t-test for weighted word (in-task):
```{r}
result_word_weighted2 <- t.test(data2 %>% filter(condition == "PC") %>% pull(word_weighted),
                      data2 %>% filter(condition == "Mask") %>% pull(word_weighted), paired = TRUE) %>%
  tidy()
```

effect size for weighted word:
```{r}
cohensD(data2 %>% filter(condition == "PC") %>% pull(word_weighted),
                      data2 %>% filter(condition == "Mask") %>% pull(word_weighted),method="paired")
```

t-test for speed (pre-task):
```{r}
result_prespeed2 <- t.test(data2 %>% filter(condition == "PC") %>% pull(PreSpeed),
                      data2 %>% filter(condition == "Mask") %>% pull(PreSpeed), paired = TRUE) %>%
  tidy()
```

effect size for speed (pre-task):
```{r}
cohensD(data2 %>% filter(condition == "PC") %>% pull(PreSpeed),
                      data2 %>% filter(condition == "Mask") %>% pull(PreSpeed),method="paired")
```
write.csv(data,"/Users/simonsheng/HMDVR_Attention_Research/Data/Result/data.csv",row.names=FALSE)
write.csv(data_long,"/Users/simonsheng/HMDVR_Attention_Research/Data/Result/data_long.csv",row.names=FALSE)
write.csv(data2,"/Users/simonsheng/HMDVR_Attention_Research/Data/Result/data2.csv",row.names=FALSE)
write.csv(group_means,"/Users/simonsheng/HMDVR_Attention_Research/Data/Result/group_means.csv",row.names=FALSE)
write.csv(result_prespeed,"/Users/simonsheng/HMDVR_Attention_Research/Data/Result/result_prespeed.csv",row.names=FALSE)
write.csv(result_word,"/Users/simonsheng/HMDVR_Attention_Research/Data/Result/result_word.csv",row.names=FALSE)
write.csv(result_word_weighted,"/Users/simonsheng/HMDVR_Attention_Research/Data/Result/result_word_weighted.csv",row.names=FALSE)
write.csv(summary,"/Users/simonsheng/HMDVR_Attention_Research/Data/Result/summary.csv",row.names=FALSE)
